Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-02-02 aggregation/agg-multioutput.tex
tweeeeeeak

Here an alternate activity, namely electrolysis of water, is specified for liquid hydrogen production and is specified at index 3 in the foreground  (shown in blue).  The inventory converts 9 kg of water to 1 kg of hydrogen using 50 kWh of electricity.  The hydrogen produced from the multi-output process is then (somewhat dubiously) taken to displace hydrogen produced through electrolysis by introducing a unity coefficient in row 3, column 1 of $A_f$.

>>>>

Here an alternate activity, namely electrolysis of water, is specified for liquid hydrogen production and is specified at index 3 in the foreground  (shown in blue).  The inventory converts 9 kg of water to 1 kg of hydrogen using 50 kWh of electricity.  The hydrogen produced from the multi-output process is then (somewhat dubiously) taken to displace hydrogen produced through the alternate activity by introducing a unity coefficient in row 3, column 1 of $A_f$.
